MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-07-21 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{equation}\label{u_c_load}
\begin{split}
U_{C} = \sum_{ws \in C}&{\bigg(\big((\alpha \times (A_{ws} + Et_{ws}) \\
        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)}
\end{split}
\end{equation}

>>>>

\begin{equation}\label{u_c_load}
\begin{split}
U_{C} = \sum_{ws \in C}&\bigg(\big(\alpha \times (A_{ws} + Et_{ws}) \\
        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)
\end{split}
\end{equation}
